---
title: "portfolio 7"
output: html_document
date: "2023-04-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(dplyr)
df <- read_excel("/Users/lindsaystall/Downloads/PIRUS_Public_May2020.xlsx")
df[df == -99 | df == -88] <- NA
```

```{r}
ggplot(df, aes(x = Social_Media_Frequency)) +
  geom_histogram(binwidth = 0.5, fill = "dodgerblue4", color = "black") +
  labs(title = "Social Media Frequency of Those in Terrorist Organizations",
       x = "Frequency",
       y = "Count") +
  scale_x_continuous(breaks = c(1,2,3,4,5),
                     labels = c("Rarely","Sporadically","Occasionally","Frequently","Continually")) +
  scale_y_continuous(breaks = seq(0,100,20)) +
  theme_minimal() +
  theme(legend.position = "right")
```



Of the individuals who there is evidence that online social media played a role in the individual’s radicalization and/or mobilization, most individuals engaged in social media-related activity related to radicalization and/or mobilization frequently and occasionally.

```{r}
df_filtered_RFR <- df[df$Radicalization_Far_Right == 1,]

ggplot(df_filtered_RFR, aes(x = Social_Media_Frequency)) +
  geom_histogram(binwidth = 0.5, fill = "dodgerblue4", color = "black") +
  labs(title = "Social Media Frequency of Far Right Terrorists",
       x = "Frequency",
       y = "Count") +
  scale_x_continuous(breaks = c(1,2,3,4,5),
                     labels = c("Rarely","Sporadically","Occasionally","Frequently","Continually")) +
  scale_y_continuous(breaks = seq(0,100,20)) +
  theme_minimal() +
  theme(legend.position = "right")
```

```{r}
df_filtered_RFL <- df[df$Radicalization_Far_Left == 1,]

ggplot(df_filtered_RFL, aes(x = Social_Media_Frequency)) +
  geom_histogram(binwidth = 0.5, fill = "dodgerblue4", color = "black") +
  labs(title = "Social Media Frequency of Far Left Terrorists",
       x = "Frequency",
       y = "Count") +
  scale_x_continuous(breaks = c(1,2,3,4,5),
                     labels = c("Rarely","Sporadically","Occasionally","Frequently","Continually")) +
  scale_y_continuous(breaks = seq(0,100,20)) +
  theme_minimal() +
  theme(legend.position = "right")
```


Far left terrorists use social media a lot more variably than other terrorists.


```{r}
df_filtered_RI <- df[df$Radicalization_Islamist == 1,]

ggplot(df_filtered_RI, aes(x = Social_Media_Frequency)) +
  geom_histogram(binwidth = 0.5, fill = "dodgerblue4", color = "black") +
  labs(title = "Social Media Frequency of Islamic Terrorist",
       x = "Frequency",
       y = "Count") +
  scale_x_continuous(breaks = c(1,2,3,4,5),
                     labels = c("Rarely","Sporadically","Occasionally","Frequently","Continually")) +
  scale_y_continuous(breaks = seq(0,100,20)) +
  theme_minimal() +
  theme(legend.position = "right")
```

```{r}
df_filtered_RSI <- df[df$Radicalization_Single_Issue == 1,]

ggplot(df_filtered_RSI, aes(x = Social_Media_Frequency)) +
  geom_histogram(binwidth = 0.5, fill = "dodgerblue4", color = "black") +
  labs(title = "Social Media Frequency of Single Issue Terrorists",
       x = "Frequency",
       y = "Count") +
  scale_x_continuous(breaks = c(1,2,3,4,5),
                     labels = c("Rarely","Sporadically","Occasionally","Frequently","Continually")) +
  scale_y_continuous(breaks = seq(0,100,20)) +
  theme_minimal() +
  theme(legend.position = "right")
```

```{r}
df %>%
  filter(Radicalization_Far_Right == 1) %>%
  count(Social_Media_Platform1) %>%
  mutate(Social_Media_Platform1 = factor(Social_Media_Platform1, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "21", "22", "23", "24", "25", "26", "27", "28"), labels = c("Facebook", "Twitter", "YouTube", "Vimeo", "Instagram", "Flickr", "Tumblr", "Imgur", "Snapchat", "Google Plus", "Skype", "LinkedIn", "MySpace", "4chan", "Reddit", "Ask.fm", "WhatsApp", "Surespot", "Telegram", "Kik", "Paltalk", "VK", "Diaspora", "JustPaste.it", "SoundCloud", "Personal blogging websites", "Other non-encrypted software", "Other encrypted software/unspecified encrypted software"))) %>%
  arrange(desc(n))
```
```{r}
df %>%
  filter(Radicalization_Far_Left == 1) %>%
  count(Social_Media_Platform1) %>%
  mutate(Social_Media_Platform1 = factor(Social_Media_Platform1, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "21", "22", "23", "24", "25", "26", "27", "28"), labels = c("Facebook", "Twitter", "YouTube", "Vimeo", "Instagram", "Flickr", "Tumblr", "Imgur", "Snapchat", "Google Plus", "Skype", "LinkedIn", "MySpace", "4chan", "Reddit", "Ask.fm", "WhatsApp", "Surespot", "Telegram", "Kik", "Paltalk", "VK", "Diaspora", "JustPaste.it", "SoundCloud", "Personal blogging websites", "Other non-encrypted software", "Other encrypted software/unspecified encrypted software"))) %>%
  arrange(desc(n))
```

```{r}
df %>%
  filter(Radicalization_Islamist == 1) %>%
  count(Social_Media_Platform1) %>%
  mutate(Social_Media_Platform1 = factor(Social_Media_Platform1, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "21", "22", "23", "24", "25", "26", "27", "28"), labels = c("Facebook", "Twitter", "YouTube", "Vimeo", "Instagram", "Flickr", "Tumblr", "Imgur", "Snapchat", "Google Plus", "Skype", "LinkedIn", "MySpace", "4chan", "Reddit", "Ask.fm", "WhatsApp", "Surespot", "Telegram", "Kik", "Paltalk", "VK", "Diaspora", "JustPaste.it", "SoundCloud", "Personal blogging websites", "Other non-encrypted software", "Other encrypted software/unspecified encrypted software"))) %>%
  arrange(desc(n))
```

```{r}
df %>%
  filter(Radicalization_Single_Issue == 1) %>%
  count(Social_Media_Platform1) %>%
  mutate(Social_Media_Platform1 = factor(Social_Media_Platform1, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "21", "22", "23", "24", "25", "26", "27", "28"), labels = c("Facebook", "Twitter", "YouTube", "Vimeo", "Instagram", "Flickr", "Tumblr", "Imgur", "Snapchat", "Google Plus", "Skype", "LinkedIn", "MySpace", "4chan", "Reddit", "Ask.fm", "WhatsApp", "Surespot", "Telegram", "Kik", "Paltalk", "VK", "Diaspora", "JustPaste.it", "SoundCloud", "Personal blogging websites", "Other non-encrypted software", "Other encrypted software/unspecified encrypted software"))) %>%
  arrange(desc(n))
```

Across all terrorist types, Facebook, Youtube, and Twitter were the most common social media platforms that played a role in the individual’s radicalization and/or mobilization process.







